Job Demands-Resources model components through the lens of O*NET classifications

### 2022-12-17 Submission.Rmd
revisiting n's

>>>>

```{r ncheck}

## Use this chunk to figure out n issue - 12/16/22 w/ Alicia on Zoom

## 12/16 looks like these sd's are non-zero but graphs have zeros - triple checking should be applied to graphs prior to this chunk

resource <- resource[ which(resource$sd > 0), ] 
########################################################
########################################################
##Need to triple check all of this. 
########################################################
########################################################
##checking the ns
#library(psych)
resource_ns <- psych::describe(data[c(118:144, 146:202)])
#resource_ns
#table(data$item161) # check one item to confirm ns - it is functioning correctly.

resource <- cbind(resource, resource_ns$n)
resource
